\textsc{LiveRec}: Framing Debug Protocols to Hotwire Probes

### 2023-08-10 paper/paper.tex
add dap request

By exploiting this protocol, we have created a new language parametric backend, which we have implemented for the C, Python, Java and Javascript programming languages. These languages are chosen to cover both compiled and interpreted languages. 
This backend offers an interface common to all three languages, which includes methods for starting and initialising the debugging server, loading and reloading code in the debugger, and executing a method while performing stack recording.

@@

The way the code is loaded also depends on the programming language. For Python, the code is loaded by being interpreted by the debug console during execution.
For Javascript, a line is added at the end of the imported file to export all the functions in the file as a module, which is then loaded into the KeepAliveAgent with \code{require}.
For Java, as with the JDI version, a DynamicClassLoader is used. For C, the code is loaded into shared libraries that can be added and reloaded at runtime.

>>>>

By exploiting this protocol, we have created a new language parametric backend, which we have implemented for the C, Python, Java and Javascript programming languages. These languages are chosen to cover both compiled and interpreted languages. 
This backend offers an interface common to all three languages, which includes methods for starting and initialising the debugging server, loading and reloading code in the debugger, and executing a method while performing stack recording. 
Table \ref{tab:dap-req} contains a list of the requests from the DAP that we have used to implement the interface.

\begin{table}[h]
  \centering
  \noindent\setlength\tabcolsep{4pt}%
  \begin{tabularx}{\linewidth}{ll*{2}{>{\RaggedRight\arraybackslash}X}}
    \toprule
    Request & Usage \\ [0.5ex]
    \midrule
    Initialize and Launch & Initialize the DAP server and launch the debuggee \\ 
    \addlinespace
    SetBreakpoints & Set breakpoints at location in source code \\ 
    \addlinespace
    StackTrace & Get the state of the current stacktrace \\ 
    \addlinespace
    Scops and Variables & Get the current scopes and variables in it \\ 
    \addlinespace
    Evaluate & Evaluate expression in the debugee \\ 
    \addlinespace
    Next and Continue & Request to step or continue in the debuggee \\ 
    \addlinespace
    \bottomrule
  \end{tabularx}
  \caption{DAP Requests}
  \label{tab:dap-req}
\end{table}

@@

The way the code is loaded also depends on the programming language. For Python, the code is loaded by being interpreted by the debug console during execution.
For Javascript, a line is added at the end of the imported file to export all the functions in the file as a module, which is then loaded into the KeepAliveAgent with \code{require}.
For Java, as with the JDI version, a Dynamic ClassLoader is used. For C, the code is loaded into shared libraries that can be added and reloaded at runtime.
